Model Checking Differentially Private Properties

### 2018-01-28 applications.tex
add frequency estimator

In pan privacy, data analysis mechanisms are required to respect
privacy even in their internal states~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}. 
The idea is to show reachability probabilities are similar on
neighboring observations. In the following, we model a discrete
variant of the mechanisms by Markov decision processes. We will also
specify pan privacy on our model using $\dpCTL$.

Consider monitoring events of the types $a$ and $b$ continuously. An
observation is a sequence of event types. Two obsevations are
{neighbors} if one can be obtained from the other by replacing 
event types any number of times, that is, if they are of the same
length. \bw{Later, we will consider a different definition of
neighborhood by restricting the number of replacements.} 
We would like to compute the number of event types in
observations. Hence for observations $a \cdots a$ and $b \cdots b$ of
arbitrary positive lengths, the query result is $1$; and the query
result is $2$ for other non-empty observations.

>>>>

In pan privacy, data analysis mechanisms are required to respect
privacy even in their internal states~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}. 
The idea is to show reachability probabilities are similar on
neighboring observations. In the following, we model a discrete
variant of the mechanisms by Markov decision processes. We will also
specify pan privacy in our model using $\dpCTL$.

Consider monitoring events of the types $a$ and $b$ continuously.
A sequence of event types is said to be an observation. Two
obsevations are {neighbors} if one can be obtained from the other 
by replacing event types any number of times, that is, if they are of
the same length. \bw{Later, we will consider a different definition of
neighborhood by restricting the number of replacements.} 
We would like to inquire the number of event types in
observations. For instance, the query result result is $1$ 
for observations $a \cdots a$ and $b \cdots b$ of arbitrary positive
lengths; and it is $2$ for other non-empty observations.

Based on the density estimation algorithm in \cite{DNPRY:10:PPSA}, we
consider the following mechanism for event type streams. Our mechanism
keeps a flag for each event type.

\begin{algorithm}
  \begin{algorithmic}[1]
  \Procedure{FrequencyEstimator}{}
    \State{$f_a \leftarrow 0, 1$ with probability 
      $\frac{1}{2}, \frac{1}{2}$ respectively}
    \Comment{Initialization}
    \State{$f_b \leftarrow 0, 1$ with probability
      $\frac{1}{2}, \frac{1}{2}$ respectively}
    \Match{current event type $e$}
    \Comment{Processing}
        \Case{$a$}
          \State{$f_a \leftarrow 0, 1$ with probability
            $\frac{3}{8}, \frac{5}{8}$ respectively}
        \EndCase
        \Case{$b$}
          \State{$f_b \leftarrow 0, 1$ with probability
            $\frac{3}{8}, \frac{5}{8}$ respectively}
        \EndCase
    \EndMatch
    \Match{$f_a + f_b$}
    \Comment{Output}
      \Case{0}
        \State{$\mathit{out} \leftarrow 0, 1, 2$ with probability
          $\frac{2}{3}, \frac{1}{6}, \frac{1}{6}$ respectively}
      \EndCase
      \Case{1}
        \State{$\mathit{out} \leftarrow 0, 1, 2$ with probability
          $\frac{1}{3}, \frac{1}{3}, \frac{1}{3}$ respectively}
      \EndCase
      \Case{2}
        \State{$\mathit{out} \leftarrow 0, 1, 2$ with probability
          $\frac{1}{6}, \frac{1}{6}, \frac{2}{3}$ respectively}
      \EndCase
    \EndMatch
    \State{\Return $\mathit{out}$}
  \EndProcedure
  \end{algorithmic}
  \caption{FrequencyEstimator}
  \label{algorithm:frequency-estimator}
\end{algorithm}
